\documentclass[11pt, a4paper]{article} %Sets the default text size to 11pt and class to article.
\usepackage{hyperref}
%-------------------------------------------------------------------------------
\topmargin=0.0in %length of margin at the top of the page (1 inch added by default)
\oddsidemargin=0.0in %length of margin on sides for odd pages
\evensidemargin=0in %length of margin on sides for even pages
\textwidth=6.5in %How wide you want your text to be
\marginparwidth=0.5in
\headheight=0pt %1in margins at top and bottom (1 inch is added to this value by default)
\headsep=0pt %Increase to increase white space in between headers and the top of the page
\textheight=9.0in %How tall the text body is allowed to be on each page
\pagenumbering{gobble} %Remove page numbers

\newcommand{\tinybullet}{ {\tiny \textbullet} }
\newcommand{\tabitem}{~~\llap{\textbullet}~~}

\begin{document}
%Name
\centerline{\Huge \sc Tyler Alterio}

%Contact Information
\centerline{
(508)-314-9756 \tinybullet \hspace{1pt}
\href{mailto:tyalt1@gmail.com}{tyalt1@gmail.com} \tinybullet \hspace{1pt}
GitHub ID: \href{http://www.github.com/tyalt1}{tyalt1}
}

\noindent \line(1,0){470}\\

%Education
\noindent {\Large \bf Education}
\smallskip \\
University of Massachusetts Lowell - Summer 2016 \\
B.S. Electrical Engineering and B.S. Computer Science
\hfill {\it GPA: $3.486$ \tinybullet \hspace{1pt} Dean's List All Semesters}

\noindent \line(1,0){470}\\

%Professional Work Experience
\noindent {\Large \bf Professional Work Experience}
\vspace{5pt}

\centerline{\bf Plexxi, Inc. \tinybullet \hspace{1pt} Nashua, NH \hfill June 2016 to Present}
\leftline{\bf Software Engineer}
\begin{itemize}
\itemsep0em
	\item Implemented Bidirectional Forwarding Detection protocol in Erlang for agile networking.
	\item Refactoring of legacy code into OTP (Erlang) applications, using test driven development.
	\item Development of REST API to access services on switch, using Swagger framework.
	\item Consulted on fullstack interaction between Python backend and switch services.
\end{itemize}

\centerline{\bf University of Massachusetts \tinybullet \hspace{1pt} Lowell, MA \hfill August 2015 to December 2015}
\leftline{\bf Research Assistant}
\begin{itemize}
\itemsep0em
	\item Experimented with P4, an open-source domain-specific network description language.
	\item Develop method to compile P4 behavioral model into CUDA implementation.
\end{itemize}

\centerline{\bf Philips Color Kinetics \tinybullet \hspace{1pt} Burlington, MA \hfill June 2014 to January 2015}
\leftline{\bf Firmware Engineer Intern}
\begin{itemize}
\itemsep0em
	\item Practical use of Git version control and tools. In addition to Github management.
	\item Implemented new features in firmware of PIC based devices with MPLAB IDE.
	\item Created command-line utility in Qt framework to interface with fixtures via UDP.
	\item Worked with team of 8 software engineers, utilizing Agile Scrum workflow.
\end{itemize}

\noindent \line(1,0){470}\\

%Skills
\noindent {\Large \bf Skills}
\vspace{5pt}
\begin{itemize}
\itemsep0em
	\item {\bf Languages (proficent in):} C, C++, Python, Bash, Erlang
	\item {\bf Languages (exposed to):} MATLAB, Clojure, Elixir, Scala
	\item {\bf Frameworks:} Swagger (for REST APIs)
	\item {\bf Workflows:} Agile, Scrum, Test Driven Development (TDD)
	\item {\bf Operating Systems:} Linux (Debian), Mac OS X
	\item {\bf Virtualization:} Docker, VMware, VirtualBox
	\item {\bf Lab Equipment:} Oscilloscope, Multimeter, Soldering
\end{itemize}

%End
\vfill
\noindent \line(1,0){470} \\

\end{document}
